%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry} % Document margins

\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{marvosym}
\usepackage{graphicx}
\usepackage{mathptmx}

\name{Mohammad Solaiman Jawad} % Your name
\address {
          \href{mailto:msjawad@uwaterloo.ca}{msjawad@uwaterloo.ca} \\
          \href{https://www.linkedin.com/in/solaiman-jawad}{in/solaiman-jawad} \\
          \href{https://github.com/MSJawad}{github.com/MSJawad}
         }

\begin{document}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
  \vspace {0.3em}
  \begin{list}{$\cdot$}{\leftmargin=0.5em}
    \itemsep -0.3em \vspace{-0.3em}
    \item Skilled in Javascript, C++, C, Scheme, Python, R, SQL, Go, Django, Bash, Git, Keras and Tensorflow
    \item Interested in web development, infrastructure, machine learning and system performance enhancement
  \end{list}
  \vspace{0.3em}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EMPLOYMENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
  \begin{rSubsection}{The Co-Operators}
    {Jan -- Apr '19}
         {Innovation Developer (Web Development)}
         {Waterloo, ON}
       \item Built a cross platform chatbot using nodeJS that collected data for a quote generation process.
       \item Chatbot successfully increased average quote generation efficiency for advisors by {\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}450\%.
    \item Created annother intelligent, cross-platform chatbot to help company advisers hire new employees. 
    \item The chatbot was developed with NodeJS(backend) and React.js(front-end) and was able to sort questions by relevance and deliver articles, text and smart image searches.
     \item Created HTTP pipelines to implement bug trackers for several projects and connect them to Jira.
  \end{rSubsection}

	\begin{rSubsection}{BRAC University}
		{Jun -- Jul '16}
		{Analyst Intern}
		{Dhaka, BD}
		\item Evaluated results of analysis based on the response of quizzes, questionnaires, and student profiles. 
		\item Updated decision tree classifiers for a prediction model of academic success of currently enrolled students.
	\end{rSubsection}

  
\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}
  
  \begin{rSubsection}{Axys}
	  {\em {\href{https://github.com/MSJawad/AXYS}
		    {git.io/vpGt1}}}
	  {}

    \item A web platform built as a way to help developers connect with designers to collaborate on projects.
    \item Won "best use of Amazon Web Services" award at Starterhacks 2018.
      
  \end{rSubsection}

	\begin{rSubsection}{restTorrent}
		{\em {\href{https://github.com/MSJawad/restTorrent}
				{git.io/fjsVG}}}
		{}
		
		\item A rest API that uses bencode URLs to help download files, similar to how torrent files are downloaded.
		\item Uses UDP instead of traditional TCP to enable faster speeds with stable connections.
		
	\end{rSubsection}

  \begin{rSubsection}{bigRSA}
	  {\em {\href{https://github.com/MSJawad/bigRSA}
		    {git.io/vNO7D}}}
	  {}

    \item Designed an optimised program that implements the RSA cryptosystem to encrypt and decrypt messages.
    
    \end{rSubsection}
    
   \begin{rSubsection}{ANN-Bank}
	  {\em {\href{https://github.com/MSJawad/ANN-Bank-Solutions}
		    {git.io/fAzBD}}}
	  {}

    \item Implemented a neural network that was able to predict, with a 86\% testing set accuracy, which customers would leave a particular bank, given a dataset of their recent transaction history.
   
    
  \end{rSubsection}

  \begin{rMinisection}
    \item {\em Other notable projects:}
      \href{https://github.com/MSJawad/Fuzzy-Spellcheck}{\textbf{fzySpellcheck}},
      \href{https://github.com/MiltonIp/Biquadris}{\textbf{Biquadris}},
      \href{https://github.com/MSJawad/CNNandDogs}{\textbf{CNNandDogs}},      
      \href{https://github.com/MSJawad/sentimentAnalysis}{\textbf{sentimentAnalysis}},
      \href{https://github.com/MSJawad/Neural-Network}{\textbf{neuralNet}}
  \end{rMinisection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rSubsection}{University of Waterloo}
		     {Sept '17 -- Sept '22 \em (expected)}
		     {Bachelors of Mathematics, Honours}
		     {}
	\item Joint Major in Computational Mathematics and Statistics
	\item Relevant Courses: Object Oriented Programming, Functional Programming, Algorithm Design and Data Abstraction, Data Types and Structures, Logic and Computation
    \item  Recipient of the President's Scholarship
      ($95^{th}$ percentile admission average)
  \end{rSubsection}
  \begin{rMinisection}
  	\item Currently doing "Computer Science: Algorithms, Theory, and Machines", a Princeton open source course.
  \end{rMinisection}
\end{rSection} 

\end{document}
